---
title: "Economic Clustering Summary Report: Cameroon 2018"
author: "Andy Kim"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  word_document:
    reference_docx: "summaryscript_style.docx"

always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, cache = T)
```

```{r install-packages, message=F, warning=F}
library(tidyverse)
library(parallelDist)
library(haven)
library(knitr)
library(kableExtra)
library(gdtools)
```


```{r user-functions}
# Functions (run these)
top_clus_table <- function(asw_mat, n){
  mat <- asw_mat %>% 
    arrange(desc(ASW)) %>%
    slice(1:n)
  
  mat2 <- select(mat,-c(ASW))
  
  #note: need to change 4 if diff number of variables used
  new_mat <- matrix(data = NA, nrow = n, ncol = 4)
  
  names <- colnames(mat2)
  
  for(i in 1:nrow(mat)){
    new_mat[i,] <- names[which(!is.na(mat2[i,]))]
  }
  
  mat3 <- as.data.frame(cbind(mat[,1],new_mat))
  
  return(mat3)
}
print_proptable <- function(proptable){
  if(length(proptable) == 2){
    labels <- names(proptable)
    values <- proptable
    
    value1 <- values[grepl("1", labels)] %>% 
      round(3) %>% 
      `*`(100)
    
    paste0("Binary, ", value1, "% 1s (or yes)")
  } else if(length(proptable) > 8){
    #labels <- names(proptable)
    values <- proptable
    
    paste0("Binary, Mode: ", names(which.max(values)))
  }
  else{
    labels <- names(proptable)
    values <- proptable %>% 
      round(3) %>% 
      `*`(100)
    
    l_v <- data.frame(values)
    f_labels <- paste0(0:(length(labels) - 1), " (", l_v[,1], ")") # attaching factors
    f_v_labels <- paste0(f_labels, " = ", values, "%", collapse = ", \n " )
    
    paste0("Categorical, ", f_v_labels)
  }
}
clus_config <- function(data, i, tab, nCores){
  vars <- as.vector(as.matrix(tab[i,2:5]))
  labels <- plyr::mapvalues(vars,
                            from = var_to_label_df$rowname,
                            to = var_to_label_df$V1, 
                            warn_missing = F)
  
  subset_data <- data %>% select("wt", vars) 
  
  out <- clusNode(subset_data,4,nCores)
  subset_data$node <- out[[1]]$clustering %>% 
    unlist() %>% 
    as.character() %>% 
    as.factor() %>% 
    as.numeric()
  
  rel_prop <- as.matrix(table(subset_data$node)/nrow(subset_data)) %>% 
    as.data.frame() %>% 
    rownames_to_column() %>%
    `colnames<-`(c("node", "prop"))
  
  grouped <- subset_data %>% 
    unite(clus, c(vars), remove = F) %>% 
    group_by(clus) %>%
    summarise(node = unique(node),
              var1 = first(!!as.name(vars[1])),
              var2 = first(!!as.name(vars[2])),
              var3 = first(!!as.name(vars[3])),
              var4 = first(!!as.name(vars[4]))) %>% 
    arrange(node) %>% 
    select(!clus) %>% 
    merge(rel_prop) %>% 
    mutate(prop = round(prop*100, 2)) %>% 
    mutate(prop = replace(prop, duplicated(prop), NA))
  
  colnames(grouped) <- c("Cluster Group", labels, "Proportion (%)")
  
  return(grouped)
}
clusNode <- function(data, num.in.cluster, ncores){
  
  ASW<-vector()
  combi<-list()
  parD<-list()
  wcKMR<-list()
  
  if (class(unlist(data[,1]))=="numeric"){
    wt<-unlist(data[,1])
    data<-data[,-1]
  } else {
    wt<-rep(1, nrow(data))
  }
  
  p <- ncol(data)
  col_cat<-seq(1,p,1)
  combn<-utils::combn(c(1:p),num.in.cluster)
  col_indx=matrix(c("NULL"), ncol(combn), p, byrow=FALSE)
  for (i in 1:ncol(combn)){
    col_indx[i,]<- t(is.element(col_cat, combn[,i]))
    col_indx[i,][col_indx[i,]==FALSE]<- NA
    colnames(col_indx)=colnames(data)
  }
  
  combi<-data[,!is.na(col_indx[i,])]
  combi_mat<-data.matrix(combi)
  parD<-parDist(combi_mat, method =  "hamming", threads = ncores) 
  wcKMR<-WeightedCluster::wcKMedRange(parD, kvals=(5), weights=wt)
  return(list(wcKMR,combi_mat))
}
```

```{r}
#### Remember to change the title of the document to reflect the correct Country + Year
# Change country-year here
# e.g. AO11 BF1718 BN1718 BU1617 CD1314 CM18 ET19 GA12 GH19 GM1920 GN18 KM12 SL19 SN19 TZ17 ZA16

# TO FIX: Rabbits is continuous , fix all animal/continuous vars

#########
cy <- "CM18"
num_var <- 4 # number of variables used to generate clusters
num_cluster <- 5
nCores <- parallel::detectCores()

# Change paths to DHS files here
hh_path <- "./data/dhs/Cameroon_2018/CMHR71DT/CMHR71FL.DTA"
ind_path <- "./data/dhs/Cameroon_2018/CMIR71DT/CMIR71FL.DTA"
#tablepng_path <- "../summoutput_files/"
#########

# Path to the cleaned DHS file
dhspath <- paste0("./data/cleaned/", cy, "_clean.rds")

# Path to the ASW output file (updated)
#aswpath <- paste0("../asw_files/", cy, "_ASW_", num_var, "cluster.rds")
aswpath <- paste0("./data/asw/ASW_", cy, "_", num_var, "cluster.rds")

dhs <- readRDS(dhspath)
asw_mat <- readRDS(aswpath) # %>% dplyr::select(-X)

# Assign missing labels to multicat variables
for(i in 1:length(Hmisc::label(dhs))){
  if(Hmisc::label(dhs)[i] == ""){
    Hmisc::label(dhs[[i]]) <- names(dhs)[i]
  }
}

# Create dictionary of labels to variable names
var_to_label_df <- data.frame(lapply(dhs, attr, "label")) %>% 
  t() %>% 
  as.data.frame() %>% 
  rownames_to_column()

#dhs %>% filter_all(any_vars(. == 9))
```

# Summary of Data

```{r, eval = F}
paste0("Country Code-year: ", cy)
paste0("Number of observations: ", nrow(dhs))
paste0("Number of clusters: ", num_cluster)
paste0("Number of variables used: ", ncol(dhs) - 1)
paste0("Distance used: Hamming")
paste0("Variables used in the algorithm: ", paste0(names(dhs)[-1], collapse = ", "))
```
**Country Code-year:** `r cy`

**Number of observations:** `r nrow(dhs)`

**Number of clusters:** `r num_cluster`

**Number of variables used:** `r ncol(dhs) - 1`

**Distance used:** Hamming

**Variables used in the algorithm:** `r paste0(names(dhs)[-1], collapse = ", ")`

#
\pagebreak

# Top Variable Groupings (Sorted by ASW)

```{r top-cluster}
## Top cluster table
tab1 <- top_clus_table(asw_mat, 10)

# Create ASW dataframe using labels, not var names
tab1_labs <- apply(tab1[,2:5], 2, function(x){
  plyr::mapvalues(x, from = var_to_label_df$rowname, to = var_to_label_df$V1, warn_missing = F)
})

tab1_asw <- round(as.numeric(tab1[,1]),4)
tab1_clean <- cbind(c(1:length(tab1_asw)), tab1_asw, tab1_labs) %>% 
  `colnames<-`(c("Group", "ASW", "Var. 1", "Var. 2", "Var. 3", "Var. 4"))

# knitr::kable(tab1_clean, booktabs = T) %>%
#   kable_styling(full_width = T) %>% 
#   row_spec(1:nrow(tab1_clean), hline_after = T) %>% 
#   column_spec(1, "1cm")


tab1_clean.f <- tab1_clean %>% 
  as.data.frame() %>% 
  flextable::flextable() %>% 
  flextable::autofit() %>% 
  flextable::set_table_properties(layout = "autofit")

knitr::knit_print(tab1_clean.f)
```

#
\pagebreak

# Marginal Distributions

```{r}
##### Marginal Distributions 
unq.vars <- unique(as.vector(as.matrix(tab1[,-1])))

props <- subset(dhs, select = unq.vars) %>% 
  lapply(table) %>% 
  lapply(prop.table) %>% 
  lapply(print_proptable) %>% 
  as.data.frame() %>% t()

descs <- lapply(dhs, attr, "label")[unq.vars] %>% unlist()

props_top_unsorted <- table(unlist(tab1[,-1]))*10
props_top_sorted <- paste0(props_top_unsorted[match(unq.vars, names(props_top_unsorted))], "%")

marg_dist_table <- cbind(unq.vars, descs, props_top_sorted, props) %>% data.frame()
names(marg_dist_table) <- c("Variable", "Description", "% Time in Top Clusters", "Distribution")
rownames(marg_dist_table) = NULL


# knitr::kable(marg_dist_table, booktabs = T) %>%
#   kable_styling(full_width = T) %>% 
#   row_spec(1:nrow(marg_dist_table), hline_after = T) %>% 
#   column_spec(1, "1cm")
marg_dist_table.f <- marg_dist_table %>% 
  as.data.frame() %>% 
  flextable::flextable() %>% 
  flextable::autofit() %>% 
  flextable::set_table_properties(layout = "autofit")

knitr::knit_print(marg_dist_table.f)
```

```{r, warning=FALSE}
#### Cluster Configurations
group1 <- clus_config(data = dhs, i=1, tab=tab1, nCores = nCores)
#group2 <- clus_config(data = dhs, i=2, tab=tab1, nCores = nCores)
#group3 <- clus_config(data = dhs, i=3, tab=tab1, nCores = nCores)
```

#
\pagebreak

# Cluster \#1 Configuration

```{r, warning=FALSE}
options(knitr.kable.NA = '')
# knitr::kable(group1, booktabs = T) %>%
#   kable_styling(full_width = T) %>% 
#   row_spec(1:nrow(group1), hline_after = T) %>% 
#   column_spec(1, "1cm")
group1.f <- group1 %>% 
  as.data.frame() %>% 
  flextable::flextable() %>% 
  flextable::autofit() %>% 
  flextable::set_table_properties(layout = "autofit")

knitr::knit_print(group1.f)
```


#
\pagebreak

# Validation Tables

```{r, warning=F, message=F, results='hide'}
source("./input_files/EC_user_functions.R")

ind <- haven::read_dta(ind_path) 

hh <- haven::read_dta(hh_path) %>% 
  mutate(wt = ifelse(hv012 == 0, hv013, hv012)*hv005/1e+06) %>% 
  preprocess_dhsfactors_adj()


ind_vars <- c("v001", "v002", "v005")

if(c("v149") %in% names(ind)){
  ind_vars <- c(ind_vars, "v149")
}

if(all(c("v201", "v206", "v207") %in% names(ind))){
  ind$deceas = ifelse(!is.na((ind$v206+ind$v207)/ind$v201), (ind$v206+ind$v207)/ind$v201, 0)
  ind$de_cat = cut(ind$deceas, 
                 breaks = c(-0.01,0.00001,0.3399,0.6699,1),
                 labels = c("0%", "1-33%", "34-66%", "67+%"))
  ind_vars <- c(ind_vars, "deceas", "de_cat")
}

if(all(c("v326") %in% names(ind))){
  ind$health = ind$v326 %>%
    str_replace_all('1[0-9]', '0') %>%
    str_replace_all('2[0-9]', '1') %>%
    str_replace_all('3[0-9]', '1') %>%
    str_replace_all('4[0-9]', '2') %>%
    str_replace_all('9[0-9]', '2')
  ind_vars <- c(ind_vars, "health")
}

hh_subset <- hh %>%
  dplyr::select(hv001, hv002, wt, all_of(unq.vars)) #normally v106 is ha66_01

ind_subset <- ind %>%
  dplyr::select(all_of(ind_vars))

# Merge the datasets
merged_data <- merge(hh_subset, ind_subset, 
                     by.x=c("hv001", "hv002"), 
                     by.y=c("v001", "v002"), all.y=FALSE)

vars <- unlist(as.vector(tab1[1,-1])) # Using variables from the top variable grouping

subset_data <- merged_data %>% 
  select(wt, all_of(vars)) 

# rerun algorithm on the subset
out <- clusNode(subset_data, 4, ncores = 8)

# collect clustering IDs for each individual
merged_data$id <- out[[1]]$clustering %>% 
  unlist() %>% 
  as.factor() %>% 
  as.numeric()
```


```{r, warning=F, message=F, results='hide'}

if(all(c("de_cat") %in% names(merged_data))){
  dectab <- merged_data %>%
    tabyl(id, de_cat, show_missing_levels = FALSE, show_na = FALSE)

  ordered_decid <- cbind(dectab[,1],prop.table(as.matrix(dectab[,2:5]), 1)) %>% 
    as.data.frame() %>% 
    arrange(desc(`0%`)) %>% 
    select(V1) %>% 
    unlist()
  
  dectab <- dectab[match(ordered_decid, dectab$id),]
  
  dectab2 <- cbind(dectab[,1:2], rowSums(dectab[,3:5])) %>% 
  `colnames<-`(c("id", "0%", ">0%"))

  ordered_decid2 <- cbind(dectab2[,1],prop.table(as.matrix(dectab2[,2:3]), 1)) %>% 
    as.data.frame() %>% 
    arrange(desc(`0%`)) %>% 
    select(V1) %>% 
    unlist()
  
  dectab2 <- dectab2[match(ordered_decid2, dectab2$id),]
}

if(all(c("v149") %in% names(merged_data))){
  edutab <- merged_data %>%
    tabyl(id, v149, show_missing_levels = FALSE, show_na = FALSE)

  # Sorted by weighted average across each row
  ordered_eduid <- cbind(c(1:5), prop.table(as.matrix(edutab[,2:7]), 1) %*% diag(c(0:5)) %>% rowSums()) %>% 
    as.data.frame() %>% 
    arrange(desc(V2))
  
  edutab <- edutab[match(ordered_eduid$V1, edutab$id),]
}

if(all(c("health") %in% names(merged_data))){
  pritab <- merged_data %>%
   tabyl(id, health, show_missing_levels = FALSE, show_na = FALSE)
  
  ordered_priid <- cbind(pritab[,1],prop.table(as.matrix(pritab[,2:4]), 1)) %>% 
    as.data.frame() %>% 
    arrange(`0`) %>% 
    select(V1) %>% 
    unlist()
  
  pritab <- pritab[match(ordered_priid, pritab$id),]
}


```

## a.1) Using Children Deceased (Sorted by proportion of 0%)


```{r, warning=F, message=F}
if(exists("dectab")){
  dectab.f <- dectab %>%
  adorn_totals(where = "row") %>%
  adorn_percentages(denominator = "row") %>%
  adorn_pct_formatting() %>% 
  adorn_ns(position = "front") %>%
  adorn_title(
    row_name = "Cluster ID",
    col_name = "Children Deceased",
    placement = "combined") %>%
  flextable::flextable() %>% 
  flextable::footnote(i = 1, j = 1,
           ref_symbols = "*",
           value = as_paragraph(paste("The chi-squared p-value is", 
                                      round(chisq.test(dectab)$p.val,4)))) %>%
  flextable::autofit() %>% 
  flextable::set_table_properties(layout = "autofit")

knitr::knit_print(dectab.f)
}


```

## a.2) Aggregating proportions greater than 0%

\newline

```{r, warning=F, message=F}
if(exists("dectab2")){
  dectab2.f <- dectab2 %>%
    adorn_totals(where = "row") %>%
    adorn_percentages(denominator = "row") %>%
    adorn_pct_formatting() %>% 
    adorn_ns(position = "front") %>%
    adorn_title(
      row_name = "Cluster ID",
      col_name = "Children Deceased",
      placement = "combined") %>%
    flextable::flextable() %>% 
    flextable::footnote(i = 1, j = 1,
             ref_symbols = "*",
             value = as_paragraph(paste("The chi-squared p-value is", 
                                        round(chisq.test(dectab2)$p.val,4)))) %>%
    flextable::autofit()  %>% 
    flextable::set_table_properties(layout = "autofit")
  
  knitr::knit_print(dectab2.f)
}
```

#
\pagebreak

## b) Using Individual Education Level Attained (Sorted by weighted average by row)

\newline

```{r, warning=F, message=F}
if(exists("edutab")){
  edutab.f <- edutab %>%
    adorn_totals(where = "row") %>%
    adorn_percentages(denominator = "row") %>%
    adorn_pct_formatting() %>% 
    adorn_ns(position = "front") %>%
    adorn_title(
      row_name = "Cluster ID",
      col_name = "Education",
      placement = "combined") %>% 
    mutate(`W. Avg.` = round(c(ordered_eduid$V2, 
                         sum(prop.table(as.matrix(colSums(edutab[,2:7]),1)) * 0:5)),2)) %>%
    flextable::flextable() %>% 
    flextable::footnote(i = 1, j = 1, ref_symbols = "*",
                        value = as_paragraph(paste("The chi-squared p-value is",
                                        round(wtd.chi.sq(merged_data$id,
                                                         merged_data$v149,
                                                         weight = merged_data$v005)[3],4)))) %>%
    flextable::footnote(i = 1, j = 1, ref_symbols = "a",
                        value = as_paragraph(paste("0=none,1=incomplete primary, 2=primary, 3=incomplete secondary, 4=secondary, 5=higher"))) %>% 
    flextable::autofit() %>% 
    flextable::set_table_properties(layout = "autofit")
  
  knitr::knit_print(edutab.f)
}
```

#
\pagebreak

## c) Using Primary Healthcare Source (Sorted by % enrolled in public healthcare [ascending order])

\newline


```{r, warning=F, message=F}
if(exists("pritab")){
  pritab.f <- pritab %>%
    adorn_totals(where = "row") %>%
    adorn_percentages(denominator = "row") %>%
    adorn_pct_formatting() %>% 
    adorn_ns(position = "front") %>%
    adorn_title(
      row_name = "Cluster ID",
      col_name = "Primary Healthcare Source",
      placement = "combined") %>%
    flextable::flextable() %>%
    footnote(i = 1, j = 1,
             ref_symbols = "*",
             value = as_paragraph(paste("The chi-squared p-value is",
                                        round(chisq.test(pritab)$p.val,4)))) %>%
    footnote(i = 1, j = 1,
             ref_symbols = "a",
             value = as_paragraph(paste("0=public/government, 1=private, 2=other"))) %>% 
    flextable::autofit() %>% 
    flextable::set_table_properties(layout = "autofit")
  
  knitr::knit_print(pritab.f)
}
```
