---
title: "Economic Clustering Summary Report: Sierra Leone 2019"
output: 
  word_document:
    reference_docx: "summaryscript_style.docx"

always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=F, message=F, warning=F)
```

```{r install-packages}
library(tidyverse)
library(parallelDist)
library(haven)
library(knitr)
library(kableExtra)
library(gdtools)
```


```{r user-functions}
source("./input_files/EC_user_functions.R")
```

```{r set params and paths}
cy <- "SL19" # country-year code
num_var <- 4 # number of variables used to generate clusters
num_cluster <- 5 # predetermined number of groups (clusters) made from the variables
num_results <- 10 # of variable sets to print (default: 10)
set <- 1 # variable set # used for this report (ex: set = 4 uses 4th highest ASW set)
nCores <- parallel::detectCores()

# Path to the cleaned DHS file
dhspath <- paste0("./data/cleaned/", cy, "_clean.rds")

# Path to the ASW output file
aswpath <- paste0("./data/asw/ASW_", cy, "_", num_var, "cluster.rds")

# Paths to raw DHS files here
hh_path <- "~/Box/Project 1/DHS Data/SIERRA LEONE 2019/SLHR7ADT/SLHR7AFL.DTA"
ind_path <- "~/Box/Project 1/DHS Data/SIERRA LEONE (SL)  2019/SLIR7ADT/SLIR7AFL.DTA"
```

```{r read data}
# read in cleaned DHS file
dhs <- readRDS(dhspath)

# read in ASW analysis file
asw_mat <- readRDS(aswpath)

# load in DHS datasets
hh <- haven::read_dta(hh_path) %>% 
  # filter(any steps taken in the cleaning_CY.Rmd file)
  preprocess_dhsfactors_adj() %>% 
  dplyr::filter(hv237 != 8) %>% 
  mutate(wt = ifelse(hv012 == 0, hv013, hv012)*hv005/1e+06)

if(nrow(dhs) != nrow(hh))
  stop("Error: No. observations in original DHS dataset must match no. observations in the 
        cleaned HH DHS file. Check cleandata_CY.R file for filtering steps and add them here.")

ind_subset <- haven::read_dta(ind_path) %>% 
  clean_individual_dhs()

# Assign missing labels to multicat variables
dhs <- reassign_label(dhs)

# Create data dictionary of DHS labels
dhs_labels <- create_label_df(dhs)
```

# Data Summary

**Country Code-year:** `r cy`

**Number of observations:** `r nrow(dhs)`

**Number of variables used:** `r ncol(dhs) - 1`

**Variable set used:** `r paste0(set)`

**Variables used in the algorithm:** `r paste0(names(dhs)[-1], collapse = ", ")`

#
\pagebreak

# Top `r num_results` Variable Sets (Sorted by ASW)

```{r top variable}
top_varset_table <- print_top_varsets(asw_mat = asw_mat, 
                                      num_results = num_results, 
                                      label_df = dhs_labels)[[1]]

# Save DHS codes
top_dhscode_table <- print_top_varsets(asw_mat = asw_mat, 
                                       num_results = num_results, 
                                       label_df = dhs_labels)[[2]]
unq.dhscodes <- unique(as.vector(top_dhscode_table))

# Format for display
top_varset_table.f <- top_varset_table %>% 
  as.data.frame() %>% 
  flextable::flextable() %>% 
  flextable::autofit() %>% 
  flextable::set_table_properties(layout = "autofit")

knitr::knit_print(top_varset_table.f)
```


#
\pagebreak

# Marginal Distributions

```{r marg dists}
marg_dists <- print_margdists(data = dhs,
                              code_mat = top_dhscode_table)

# Format for display
marg_dists.f <- marg_dists %>% 
  as.data.frame() %>% 
  flextable::flextable() %>% 
  flextable::autofit() %>% 
  flextable::set_table_properties(layout = "autofit")

knitr::knit_print(marg_dists.f)
```


#
\pagebreak

# Cluster Configuration (Set #`r set`)

```{r cluster dist}
cluster_dist <- print_clus_dist(data = dhs, 
                                set = set, 
                                code_mat = top_dhscode_table, 
                                label_df = dhs_labels, 
                                nCores = nCores)

# For printing
cluster_dist_df <- cluster_dist[[1]]

# For validation step
cluster_dist_ids <- cluster_dist[[2]]

cluster_dist_df.f <- cluster_dist_df %>% 
  as.data.frame() %>% 
  flextable::flextable() %>% 
  flextable::autofit() %>% 
  flextable::set_table_properties(layout = "autofit")

knitr::knit_print(cluster_dist_df.f)
```

#
\pagebreak

# Validation Tables

```{r val tables}
# create merged HH and Individual dataset
merged_dhs <- hh %>% 
  select(hv001, hv002, wt, all_of(unq.dhscodes)) %>% 
  mutate(id = cluster_dist_ids) %>% 
  merge(ind_subset, 
        by.x=c("hv001", "hv002"), 
        by.y=c("v001", "v002"), all.y=FALSE)

val_tables <- create_validation_tables2(merged_data = merged_dhs)
```

## a.1) Using Children Deceased (Sorted by proportion of 0%)

```{r dec tab}
# The tables below all have flexible formatting options

if("dectab" %in% names(val_tables)){
  dectab.f <- val_tables$dectab %>%
    adorn_totals(where = "row") %>%
    adorn_percentages(denominator = "row") %>%
    adorn_pct_formatting() %>% 
    adorn_ns(position = "front") %>%
    adorn_title(
      row_name = "Cluster ID",
      col_name = "Children Deceased",
      placement = "combined") %>%
    flextable::flextable() %>% 
    flextable::footnote(i = 1, j = 1,
             ref_symbols = "*",
             value = as_paragraph(paste("The chi-squared p-value is", 
                                        round(chisq.test(val_tables$dectab)$p.val,4)))) %>%
    flextable::autofit() %>% 
    flextable::set_table_properties(layout = "autofit")

  knitr::knit_print(dectab.f)
}
```


## a.2) Aggregating proportions greater than 0%

\newline

```{r dec2 tab}
if("dectab2" %in% names(val_tables)){
  dectab2.f <- val_tables$dectab2 %>%
    adorn_totals(where = "row") %>%
    adorn_percentages(denominator = "row") %>%
    adorn_pct_formatting() %>% 
    adorn_ns(position = "front") %>%
    adorn_title(
      row_name = "Cluster ID",
      col_name = "Children Deceased",
      placement = "combined") %>%
    flextable::flextable() %>% 
    flextable::footnote(i = 1, j = 1,
             ref_symbols = "*",
             value = as_paragraph(paste("The chi-squared p-value is", 
                                        round(chisq.test(val_tables$dectab2)$p.val,4)))) %>%
    flextable::autofit()  %>% 
    flextable::set_table_properties(layout = "autofit")
  
  knitr::knit_print(dectab2.f)
}
```

#
\pagebreak

## b) Using Individual Education Level Attained (Sorted by weighted average by row)

\newline

```{r education tab}
if("edutab" %in% names(val_tables)){
  edutab.f <- val_tables$edutab %>%
    adorn_totals(where = "row") %>%
    adorn_percentages(denominator = "row") %>%
    adorn_pct_formatting() %>% 
    adorn_ns(position = "front") %>%
    adorn_title(
      row_name = "Cluster ID",
      col_name = "Education",
      placement = "combined") %>% 
    mutate(`W. Avg.` = round(c(val_tables$ordered_eduid$V2, 
                         sum(prop.table(as.matrix(colSums(val_tables$edutab[,-1]),1)) * 0:5)),2)) %>%
    flextable::flextable() %>% 
    flextable::footnote(i = 1, j = 1, ref_symbols = "*",
                        value = as_paragraph(paste("The chi-squared p-value is",
                                        round(wtd.chi.sq(merged_dhs$id,
                                                         merged_dhs$v149,
                                                         weight = merged_dhs$v005)[3],4)))) %>%
    flextable::footnote(i = 1, j = 1, ref_symbols = "a",
                        value = as_paragraph(paste("0=none, 1=incomplete primary, 2=primary, 3=incomplete secondary, 4=secondary, 5=higher"))) %>% 
    flextable::autofit() %>% 
    flextable::set_table_properties(layout = "autofit")
  
  knitr::knit_print(edutab.f)
}
```

#
\pagebreak

## c) Using Primary Healthcare Source (Sorted by % enrolled in public healthcare [ascending order])

\newline


```{r private health tab}
if("pritab" %in% names(val_tables)){
  pritab.f <- val_tables$pritab %>%
    adorn_totals(where = "row") %>%
    adorn_percentages(denominator = "row") %>%
    adorn_pct_formatting() %>% 
    adorn_ns(position = "front") %>%
    adorn_title(
      row_name = "Cluster ID",
      col_name = "Primary Healthcare Source",
      placement = "combined") %>%
    flextable::flextable() %>%
    footnote(i = 1, j = 1,
             ref_symbols = "*",
             value = as_paragraph(paste("The chi-squared p-value is",
                                        round(chisq.test(val_tables$pritab)$p.val,4)))) %>%
    footnote(i = 1, j = 1,
             ref_symbols = "a",
             value = as_paragraph(paste("0=public/government, 1=private, 2=other"))) %>% 
    flextable::autofit() %>% 
    flextable::set_table_properties(layout = "autofit")
  
  knitr::knit_print(pritab.f)
}
```

